Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-08 src/tex/ms.tex
Add section about pp plot

In order to verify the fidelity of the sampler, we can inject a signal
into the parameter estimation pipeline and compared the recovery parameters to
the true parameters.

% Show injection pp plot

\subsection{Real event parameter estimation}

@@

% Compared to other works
There are recent works from different groups on speeding up parameter estimation
of gravitational wave, including efficient reparameterization and deep learning
\kw{cite}. While all of these methods are able to get down to minutes-scale parameter
estimation with high fidelity, we would like to highlight the unique strength of
this work, and potential interplay between our work and other's work.
% Stephen's work
Compared to \kw{Stephan's paper}, we do not rely on pre-training the
neural network on a large collection of waveforms and noise realization. This
means as soon as new waveforms models and noise models are available, our
algorithm can already be deployed. Furthermore, our method is essentially an
MCMC algorithm, which inherits the merit of convergence measures in MCMC. As we
are only using the normalizing flow as a proposal distribution, and the
normalizing flow is trained jointly with a local sampler, we do not suffer from
overfitting since our data is always approaching the target distribution, in
this sense, we do not introduce potential extra systematic error to inference
result.

>>>>

To demonstrate the robustness of our pipeline, we use it to recover the
parameters of a set of simulated signals. We create a set of simulated signals
and inject them into simulated noise, generated under the Gaussian noise
assumption using the designed PSD for every detector. Then we run our pipeline
given the simulated data and determine the credible interval at the true
parameters of the injected signals. Given the set of credible value, we can
check whether the true value lies within a certain credible interval at a
reasonable frequency. If our pipeline is perfect, we should find the true
parameters lie within $x\%$ credible interval $x\%$ of the time, e.g. the true
value should lie within the $50\%$ credible interval $50\%$ of the time.
Deviation from this behavior suggests the pipeline is either over-confident or
too conservative.

% State the distribution of injected population
We sample 1000 events from the following distribution of parameters:

% Show injection pp plot
To quantify the accuracy of our pipeline, we show th
\subsection{Real event parameter estimation}

@@

% Compared to other works
There are recent works from different groups on speeding up parameter estimation
of gravitational wave, including efficient reparameterization and deep learning
\kw{cite}. While all of these methods are able to get down to minutes-scale parameter
estimation with high fidelity, we would like to highlight the unique strength of
this work, and potential interplay between our work and other's work.
% Stephen's work
Compared to \kw{Stephan's paper}, we do not rely on pre-training the
neural network on a large collection of waveforms and noise realization. This
means as soon as new waveforms models and noise models are available, our
algorithm can already be deployed. Furthermore, our met hod is essentially an
MCMC algorithm, which inherits the merit of convergence measures in MCMC. As we
are only using the normalizing flow as a proposal distribution, and the
normalizing flow is trained jointly with a local sampler, we do not suffer from
overfitting since our data is always approaching the target distribution, in
this sense, we do not introduce potential extra systematic error to inference
result.
